---
title: "Extending ggplot2"
author: chull companion guide
output: html_document
---


```{r setup, include = F}
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
options(knitr.duplicate.label = "allow")
knitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = "", cache = T, error = F)
library(flipbookr)
library(tidyverse)
```

# A1. Here is some code (I'm naming the chunk "my_code"): 

You might think about setting this code chunk's option include = F, to hide the code and output.

```{r my_code, include=F}
A <- ggproto("A", NULL,
  x = 1,
  inc = function(self) {
    self$x <- self$x + 1
  }
)

A$x
A$inc()
A$x
A$inc()
A$inc()
A$x
```



# A2. Let's get a walk-through using embed_flipbook():

You might want to set the code chunk options to echo = F, unless you are demoing embed_flibook(). 

```{r}
embed_flipbook(chunk_name = "my_code", 
                       use_share_again = T,
                       font_size = 120)
```

---

# B1. Here is some more code; I'm named the code chunk "fine_tuning":

You might just set the code chunk options include = F.

```{r fine_tuning, fig.show='hide'}
StatChull <- ggproto("StatChull", Stat,
  compute_group = function(data, scales) {
    data[chull(data$x, data$y), , drop = FALSE]
  },
  
  required_aes = c("x", "y")
)

library(magrittr)
cars %$% 
  # identify the exterior chull points row number
  chull(x = speed, y = dist)

cars[chull(cars$speed, cars$dist), , drop = F]


stat_chull <- function(mapping = NULL, data = NULL, geom = "polygon",
                       position = "identity", na.rm = FALSE, show.legend = NA, 
                       inherit.aes = TRUE, ...) {
  layer(
    stat = StatChull, data = data, mapping = mapping, geom = geom, 
    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
    params = list(na.rm = na.rm, ...)
  )
}


cars %>% 
  ggplot(aes(speed, dist)) +
  geom_point() +
  stat_chull(fill = NA, color = "black") ->
cars_ggplot

ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  stat_chull(fill = NA, color = "black") +
  stat_chull(fill = NA) +
  aes(color = drv) +
  stat_chull(geom = "point", size = 4, 
             colour = "red") +
  stat_chull(geom = "point", size = 4)
```

# B2. Let's look at the build created from  embed_flipbook. View below or view [in new tab](fine_tuning.html){target="_blank"}

You might set the code chunk option echo = F

```{r, eval = T}
embed_flipbook(chunk_name = "fine_tuning", 
               widths = c(1,1),
               use_share_again = T, 
               use_embed_xaringan = T,
               font_size = 65,
               title_page = T,
               title = "id chull points",
               subtitle = "Thematic Adjustments",
               author = "extending ggplot2 example")
```

# geom

```{r geom}
GeomSimplePoint <- ggproto("GeomSimplePoint", Geom,
  required_aes = c("x", "y"),
  default_aes = aes(shape = 19, colour = "black"),
  draw_key = draw_key_point,

  draw_panel = function(data, panel_params, coord) {
    coords <- coord$transform(data, panel_params)
    grid::pointsGrob(
      coords$x, coords$y,
      pch = coords$shape,
      gp = grid::gpar(col = coords$colour)
    )
  }
)

geom_simple_point <- function(mapping = NULL, data = NULL, stat = "identity",
                              position = "identity", na.rm = FALSE, show.legend = NA, 
                              inherit.aes = TRUE, ...) {
  layer(
    geom = GeomSimplePoint, mapping = mapping,  data = data, stat = stat, 
    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
    params = list(na.rm = na.rm, ...)
  )
}

ggplot(mpg, aes(displ, hwy)) + 
  geom_point() +
  geom_simple_point()
```


```{r}
embed_flipbook("geom")
```



```{r}
StatChull <- ggproto("StatChull", Stat,
  compute_group = function(data, scales) {
    data[chull(data$x, data$y), , drop = FALSE]
  },
  
  required_aes = c("x", "y")
)

GeomPolygonHollow <- ggproto("GeomPolygonHollow", GeomPolygon,
  default_aes = aes(colour = "black", fill = NA, size = 0.5, linetype = 1,
    alpha = NA)
  )
geom_chull <- function(mapping = NULL, data = NULL, 
                       position = "identity", na.rm = FALSE, show.legend = NA, 
                       inherit.aes = TRUE, ...) {
  layer(
    stat = StatChull, geom = GeomPolygonHollow, data = data, mapping = mapping,
    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
    params = list(na.rm = na.rm, ...)
  )
}

ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  geom_chull() +
  aes(color = factor(cyl))
```

---


```{r}
StatXmean <- ggproto("StatXmean", Stat,
  compute_group = function(data, scales) {
    mean(data$x) %>% 
      tibble(x = .)
  },
  
  required_aes = c("x")
)

GeomSegmentV <- ggproto("GeomSegmentV", GeomSegment,
  default_aes = aes(colour = "black", size = 0.5, linetype = 1, y = -Inf, yend = Inf,
    alpha = NA)
  )
geom_xmean <- function(mapping = NULL, data = NULL, 
                       position = "identity", na.rm = FALSE, show.legend = NA, 
                       inherit.aes = TRUE, ...) {
  layer(
    stat = StatChull, geom = GeomPolygonHollow, data = data, mapping = mapping,
    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
    params = list(na.rm = na.rm, ...)
  )
}

ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  geom_chull() +
  aes(color = factor(cyl))
```




# C. Okay python!  Just kidding.  This doesn't work yet.

---





```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 80%}

@media print {
  .has-continuation {
    display: block;
  }
}
```
