---
title: "The Rose"
author: "Gina Reynolds, June 2021"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:10
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r, include = F}
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
knitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = "", cache = T)
library(flipbookr)
library(tidyverse)
```

`r chunk_reveal("the_rose", break_type = 1, display_type = "output", chunk_options = "fig.align = 'center', out.width = '75%'")`

---
class: inverse

I saw the rose posted recently by Antonio Sánchez Chinchón @aschinchon.  

I liked what I was looking at, but didn't really 'get' what was going on - even with the code posted alongside.

I used that and other code posted by Alex as the basis for exploring w/ ggplot2 and flipbookr: https://cpastem.caltech.edu/documents/18024/ARt.nb.html


---
class: inverse

# Overview

## The rose/flower is ...

--

- a grid of points

--

- where x positions are offset based on the sin of y

--

- and y positions are offset based on the cos of x

--

- and the coordinate system is polar.

--

- Also, the sin and cosine waves accelerate


---
class: inverse

# First the x position. 

## the x grid position is offset ...

- into a wave based on the sin of y

--

- and the waves accelerate moving away from the x axis, so actually y^2

--

- *in ggplot2 updating x positions by overwriting with aes(x = ?) statements*

--

- and the pattern is reflected across the x axis

--

- *adding a geom_point layer where the sign of y is negative*



---


`r chunk_reveal("rose_x_shift")`

```{r rose_x_shift, include = F}
seq(0, 4, by = .1) -> 
  my_seq

tibble(x = my_seq) %>% 
  crossing(y = my_seq) %>% 
  ggplot() +
  aes(x = x, 
      y = y) +
  geom_point(alpha = .5) +
  aes(color = y) +
  scale_color_viridis_c() +
  aes(x = x - sin(y)) +
  scale_y_continuous(
    breaks = -2:2/2*pi, 
    labels = paste(-2:2/2, "pi")
    ) +
  # where waves are accelerating
  aes(x = x - sin(y^2)) +
  scale_y_continuous(breaks = c((0:9/2*pi)^.5,-(0:9/2*pi)^.5),
                     labels = paste0(c((0:9/2),-(0:9/2)), "^.5 pi")) +
  # and reflected over y = 0
  geom_point(
    data = . %>% mutate(y = -y),
    alpha = .5) ->
x_offset_determined_by_y
```


---
class: inverse

# Now the y position.

## the y grid position is offset ...

- into a wave based on the cosine of x

--

- and the waves accelerate moving away from x = 0 (so we actually use x^2)

--

- and the pattern is reflected across x = 0




---


`r chunk_reveal("rose_y_shift")`

```{r rose_y_shift, include = F}
tibble(x = my_seq) %>% 
  crossing(y = my_seq) %>% 
  ggplot() +
  aes(x = x, 
      y = y) +
  geom_point(alpha = .5) +
  aes(color = y) +
  scale_color_viridis_c() +
  aes(y = y - cos(x)) +
  # where waves are accelerating
  aes(y = y - cos(x^2)) +
  # and reflected over y = 0
  geom_point(
    data = . %>% mutate(x = -x),
    alpha = .5) ->
y_offset_determined_by_x
```

---
class: inverse


# putting it all together

--

- let's see the evolution of both both sets of offsets...

--

- we also let the squaring handle the symmetry across the x and y axes (the sequence goes from -3 to positive 3)

--

---

`r chunk_reveal("the_rose_lite")`

```{r the_rose_lite, include = F}
seq(-4, 4, by = .1) -> 
  my_seq
  
tibble(x = my_seq) %>% 
  crossing(y = my_seq) %>% 
  ggplot() +
  aes(x = x, 
      y = y) +
  geom_point(alpha = .5) +
  aes(color = y) +
  scale_color_viridis_c(option = "cividis") +
  # offset of x is determined by sin of y
  aes(x = x - sin(y)) +
  # offset of y is determined by cos of x
  aes(y = y - cos(x)) +
  # and waves are accelerating 
  # moving away from zero so use squared value
  aes(x = x - sin(y^2)) +
  aes(y = y - cos(x^2)) +
  theme_void() + 
  coord_polar() 
```


---
class: inverse

# Higher resolution is a lot prettier

--

- grid points are closer together and smaller

--

- patterns are clearer in less dense regions

--

- Also, I just do sequence from -3 to 3.  This range be more classic, but I though from -4 to 4 showed wave 'acceleration' more clearly. 



---

`r chunk_reveal("the_rose")`

---
class: inverse

```{r, include = F}
replacements = c("inferno", "magma", "viridis", "cividis")
#r chunk_reveal("the_rose", break_type = "replace", replace = "magma", replacements = replacements)`
```

# Try stuff and see what happens.

--

## We can also look a decelaration of waves away from zero and slower accelarations

--

- squaring is a special case that gives us reflection automatically

--

- we'll git irrational numbers if we raise negative numbers to decimals

--

- so we take absolute value first

--

- we'll only adjust the value of x based on the sin of the absolute value of y to some power (between .3 to 1.9)


---


`r chunk_reveal("the_rose", break_type = "replace", replace = "y\\^2", replacements = c("abs(y)^.3", "abs(y)^.5", "abs(y)^.7", "abs(y)^.9", "abs(y)^1", "abs(y)^1.25","abs(y)^1.5", "abs(y)^1.75", "abs(y)^1.9"))`


---


```{r the_rose, include = F}
seq(-3, 3, by = .01) -> my_seq
  
tibble(x = my_seq) %>% 
  crossing(y = my_seq) %>% 
  ggplot() +
  aes(x = x, 
      y = y) +
  geom_point(alpha = .05, size = .05) +
  aes(color = y) +
  scale_color_viridis_c(option = "cividis") +
  # offset of x is determined by sin of y
  aes(x = x - sin(y)) +
  # offset of y is determined by cos of x
  aes(y = y - cos(x)) +
  # and waves are accelerating 
  # moving away from zero so use squared value
  aes(x = x - sin(y^2)) +
  aes(y = y - cos(x^2)) +
  theme_void() + 
  coord_polar() +
  theme(legend.position = "none")
```

---
class: inverse, center, middle

# stingray

---




`r chunk_reveal("stingray_high_res", break_type = 1, display_type = "output", chunk_options = "fig.align = 'center', out.width = '70%'")`


---

`r chunk_reveal("stingray")`

```{r stingray, include = F}
seq(0,9, by = 0.1) ->
  my_seq

tibble(x = my_seq) %>% 
  crossing(y = my_seq) %>% 
  ggplot() +
  aes(x = x, y = y) +
  geom_point(size = .1) +
  aes(color = y) +
  aes(alpha = x) +
  scale_color_viridis_c() +
  aes(x = x + sin(y)) +
  aes(x = x + sin(y)^2) +
  aes(x = log(x) + sin(y)^2) +
  aes(y = y + sin(x)*.25) +
  aes(y = y + sin(x)*.5) +
  aes(y = y + sin(x)*.75) +
  aes(y = y + sin(x)) +
  aes(y = y + sin(x)^1.25) +
  aes(y = y + sin(x)^1.5) +
  aes(y = y + sin(x)^1.75) +
  aes(y = y + sin(x)^2) +
  aes(y = log(y) + sin(x)^2) +
  coord_equal() +
  theme_void()  +
  theme(legend.position = "none")
```

---
class: inverse, center, middle

# stingray higher res

---

`r chunk_reveal("stingray_high_res")`

```{r stingray_high_res, include = F}
seq(0,9, by = 0.025) ->
  my_seq

tibble(x = my_seq) %>% 
  crossing(y = my_seq) %>% 
  ggplot() +
  aes(x = x, y = y) +
  geom_point(size = 0, alpha = .05) +
  aes(color = y) +
  aes(alpha = x) +
  scale_color_viridis_c() +
  aes(x = x + sin(y)*.1) +
  aes(x = x + sin(y)*.3) +
  aes(x = x + sin(y)*.75) +
  aes(x = x + sin(y)) +
  aes(x = x + abs(sin(y))^1.1) +
  aes(x = x + abs(sin(y))^1.5) +
  aes(x = x + abs(sin(y))^1.75) +
  aes(x = x + sin(y)^2) +
  aes(x = log(x) + sin(y)^2) +
  aes(y = y + sin(x)*.1) +
  aes(y = y + sin(x)*.3) +
  aes(y = y + sin(x)*.75) +
  aes(y = y + sin(x)) +
  aes(y = y + abs(sin(x))^1.1) +
  aes(y = y + abs(sin(x))^1.5) +
  aes(y = y + abs(sin(x))^1.75) +
  aes(y = y + sin(x)^2) +
  aes(y = log(y) + sin(x)^2) +
  coord_equal() +
  theme_void()  +
  theme(legend.position = "none")
```


---
class: inverse, center, middle

# another rose

---




`r chunk_reveal("rosy", break_type = 1, display_type = "output", chunk_options = "fig.align = 'center', out.width = '70%'")`

---

`r chunk_reveal("rosy")`



```{r rosy, include = F}
seq(-12,12, by = 0.04) ->
  my_seq

tibble(x = my_seq) %>%   
  crossing(y = my_seq) %>% 
  ggplot() +
  aes(x = x, y = y) +
  geom_point(alpha = 0.05, 
             color = "darkred", 
             size = 0) +
  aes(x = x + .1 * sin(y)) +
  aes(x = x + .3 * sin(y)) +
  aes(x = x + .7 * sin(y)) +
  aes(x = x + 1.5 * sin(y)) +
  aes(x = x + pi * sin(y)) +
  aes(y = y + .1 * sin(x)) +
  aes(y = y + .3 * sin(x)) +
  aes(y = y + .7 * sin(x)) +
  aes(y = y + 1.5 * sin(x)) +
  aes(y = y + pi * sin(x)) +
  theme_void() +
  scale_y_reverse() +
  scale_x_continuous(limits = c(-50, 50)) +
  coord_polar() +
  scale_x_continuous(limits = c(-30, 30)) +
  scale_x_continuous(limits = c(-25, 25)) +
  scale_x_continuous(limits = c(-18, 18)) +
  scale_x_continuous()
```

---

`r chunk_reveal("dandelion", title = "Dandalion: One less deconstructed")`

```{r dandelion, include = F}
seq(-2,2, by = 0.01) ->
  my_seq

tibble(x = my_seq) %>%   
  crossing(y = my_seq) %>% 
  ggplot() +
  aes(x = x^3 - sin(y)) +
  aes(y = y^3 - cos(x)) +
  geom_point(alpha = 0.05, 
             size = 0) +
  theme_void()+
  coord_polar()+
  labs(subtitle = "Dandelion")
```


<!-- adjust font size in this css code chunk, currently 80 -->

```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 80%}

@media print {
  .has-continuation {
    display: block;
  }
}

code.r.hljs.remark-code{
  position: relative;
  overflow-x: hidden;
}


code.r.hljs.remark-code:hover{
  overflow-x:visible;
  width: 500px;
  border-style: solid;
}
```



